---
title: "CLD"
author: "Andrey"
date: "2022-11-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(pROC)
library(gtsummary)
```

## 1
```{r}
diabetes <- as_tibble(read.csv("diabetes.csv"))
diabetes %>% glimpse()
```

Removing zeroes to NA, add new colum converting glucose level to mmol/l
```{r}
diabetes <- diabetes %>% mutate(`Glucose` = `Glucose` %>% na_if(0)) %>%
  mutate(`BloodPressure` = `BloodPressure` %>% na_if(0)) %>%
  mutate(`SkinThickness` = `SkinThickness` %>% na_if(0)) %>% 
  mutate(`Insulin` = `Insulin` %>% na_if(0)) %>% 
  mutate(`BMI` = `BMI` %>% na_if(0)) %>% 
  mutate(`DiabetesPedigreeFunction` = `DiabetesPedigreeFunction` %>% na_if(0)) %>%      mutate(`Age` = `Age` %>% na_if(0)) 



diabetes <- diabetes %>% mutate(`Glucose_mmol` = round(Glucose / 18, 1)) %>% select(!`Glucose`)  

```

Number of patients with increased glucose level and with normal level
```{r}
diabetes %>% filter(`Glucose_mmol` >= 7.8) %>% nrow()  #patients with increased level
diabetes %>% filter(`Glucose_mmol` < 7.8) %>% nrow() #patients with normal level
```

##2
```{r}
diabetes <- diabetes %>% mutate(across(Outcome, ~ as.factor(.x)))
roc_curve_1 <- roc(Outcome ~ Glucose_mmol, data = diabetes, ci = T)
roc_curve_1

ggroc(roc_curve_1) + 
    theme_bw()
```

##3
```{r}
AUC = roc_curve_1$ci[2] %>% round(3)
AUC
```
##4
```{r}
AUC_lower = roc_curve_1$ci[1] %>% round(3)
AUC_upper = roc_curve_1$ci[3] %>% round(3)
AUC_lower
AUC_upper
```
##5 
```{r}
roc_curve_2 <- roc(Outcome ~ Insulin, data = diabetes, ci = T)
roc_curve_2 %>% coords()

roc_curve_2 %>% coords(x = "best", best.method = "closest.topleft")

```
##6
```{r}
AUC_diabetes <- diabetes %>% 
    pivot_longer(cols = !Outcome) %>% 
    group_by(name) %>% 
    summarise(AUC = roc(Outcome, value, ci = T)$ci[2] %>% round(3),
              AUC_LCL = roc(Outcome, value, ci = T)$ci[1] %>% round(3),
              AUC_UCL = roc(Outcome, value, ci = T)$ci[3] %>% round(3))
AUC_diabetes
```

Find the biggest and the smallest AUC
```{r}
biggest <- AUC_diabetes %>% filter(`AUC` == max(`AUC`, na.rm = T))
biggest 

small <- AUC_diabetes %>% filter(`AUC` == min(`AUC`, na.rm = T))
small 
```
So we can say that the glucose level is the best numeric feature for diagnostic informativity. And the most lower level of diagnostic informativity has the diabetes pedigree function feature. 
